Measuring background and systemic risks in finance

### 2015-05-31 srisk4.tex
wc/pdj changes

@@

% Title of paper
\title{Measuring background risk and systemic risk in finance}
% List of authors, with corresponding author marked by asterisk
\author{Piet de Jong,  Geoff Loudon and Weihao Choo \\[4pt]
% Author addresses
\textit{Department of Applied Finance and Actuarial Studies\\ Macquarie University, Sydney, NSW 2109.}
\\[2pt]
%E-mail address for correspondence
{piet.dejong@mq.edu.au}}

@@

Recent literature in the area of quantitative systemic stress measurement includes 
\cite{adrian2011covar},
\cite{acharya2012capital},
\cite{acharya2012measuring},
 \cite{brownlees2010volatility} and \cite{brownlees2015}.   The proposed research aims to extend and apply these techniques particularly in relation to the entities regulated by APRA.   Thus our  broad aim is to develop, implement and bring to bear recent developments in stress testing  on the aims of APRA and the CIFR targeted research areas.   (This needs much more commentary).

@@

@@

\section{Capital shortfall and leverage}

If $d_{it}$ and $w_{it}$ are the debt and equity of a firm $i$ at time $t$ and $\kappa$ is the capital requirement,  then the capital shortfall at time $t$ is 
\be{shortfall}
\kappa(d_{it}+w_{it}) - w_{it} = \kappa d_{it}  - (1-\kappa) w_{it} = \kappa d_{it}\left(1-\e^{-\ell_{it}}\right)\ ,
\ee
where 
$$
\ell_{it} \equiv  \ln\frac{\kappa d_{it}}{(1-\kappa)w_{it}}= \ln\frac{d_{it}}{w_{it}}+\logit(\kappa) \cq \logit(\kappa)\equiv \ln \frac{\kappa}{1-\kappa} \ .
$$
The quantity $\ell_{it}$ is called   adjusted log--leverage and $\ell_{it}>0$ implies capital shortfall \eref{shortfall} is positive.
Basel II assumes\footnote{See for example \cite{brownlees2015}.   The value of $\kappa$ can and is varied to test for sensitivity etc.} 
 $\kappa=0.08$ implying $\logit(\kappa)=-2.44$ and  $\ell_{it}$ is the actual log--leverage minus 2.44.   
As the actual  log leverage of a firm  increases to 2.44, the firm approaches a Basel breach.

\fref{Bloglev} displays Basel log--leverages for the four major and four minor Australian banks listed in \tref{banks} on the first trading day of each month from January 2003  through to December 2014.  Note most banks are Basel compliant up to about 2008.

\begin{figure}[htbp]
\begin{center}
\label{Bloglev}
\includegraphics{figures/bloglev.pdf}
\caption{Adjusted log--leverages for four major (left panel) and four minor (right panel) Australian banks from the beginning of 2003 through to end of 2014.  All banks contravene the threshold (corresponding to the zero horizontal) around the start of 2009.}
\end{center}
\end{figure}

\section{Future capital shortfall}

Financial institutions and regulators are concerned with future Basel compliance and in assessing  the likelihood of a  future Basel breach.   Future compliance depends on the future return on equity.   Consider  firm $i$ at time  $t+h$ where $h>0$.  Then\footnote{In the further development $\e^\nu$ is the continuously compounded return and $\nu$  the  rate of return or log return.}
$$
\ell_{i,t+h} = \ln \frac{d_{i,t+h}}{w_{i,t+h}} +\logit(\kappa)= \ell_{it} -\nu_{it}\cq \nu_{it}\equiv \ln\frac{w_{i,t+h}}{w_{it}}  \ ,
$$
where it is assumed $d_{i,t+h}=d_{it}$.  Hence $\nu_{it}$ is the log return on equity over $(t,t+h)$.  The future return is unknown at time $t$ but its distribution may be  well understood.

The capital  shortfall  at time $t+h$ is,
\be{bs}
\kappa d_{it} |1-\e^{\nu_{it}-\ell_{it}}|^+\cq  |x|^+\equiv \max(0,x)\ . 
\ee
Thus shortfall \eref{bs} is a put on the return $\e^{\nu_{it}-\ell_{it}}$  with strike 1.  
The Basel  limit is reached at $t+h$ if $\nu_{it}=\ell_{it}$ and  breached  if
$\nu_{it}< \ell_{it}$.
A breach is  unlikely if $\ell_{it}$ is low i.e. either the log--leverage is low, or the  constant $\kappa$ in the calculation of $\ell_{it}$ is low.

If there is a breach, $\nu_{it}<\ell_{it}$, then the amount in \eref{bs} makes up for the shortfall.   This amount may be cold comfort to regulators as it leaves the firm in a precarious position, teetering on the edge of non--compliance.

@@

To illustrate the setup, \fref{simulation}   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.    Both panels use the same horizontal and vertical scales.   Thus based on the available data at those two points in  time, policy makers and regulators faced entirely different projections based on the same time series model.   The scatter of dots are the forward simulations.  Note there is no lookahead bias as the model at each time point is based on the available data to that point in time.    The red horizontal line in each panel indicates the projected Basel limit:  any firm return less than the limit would constitute a Basel breach.   In the left panel there is little confidence that the Basel limit will be reached since it requires a return on equity approaching 20\% -- with confidence less than xxx the Basel standard will be breached.  In the right panel there is no chance of a Basel breach under any of the projected return on equity view -- the bank is ``safe."

 The black dots in each panel indicate the actual outcome after one month.    In the left panel the outcome is a decline in both  the market and stock price.    In the right panel the returns are xxx and xxx.    Thus at the beginning of January  2009 the CBA bank was projected to be far from compliance in one month's time  while in December 2015 the one month projection is of complete compliance.

 The two panels  display very different volatility and slopes.  These snapshots are used to compute systemic stress.

\begin{figure}[htbp]
\begin{center}
\includegraphics{figures/simulation.pdf}
\caption{Forecast bivariate distribution of one month forward rates of return   for CBA (vertical axis) and the market rate of return (horizontal axis) at start of January 2009 (left panel)  and December 2014 (right panel). Note scales in both panels are the same, the relatively large volatility in the left panel, and the left skew in the  marginal distributions.  Yellow and black dot in each panel indicate origin (0,0) and  realized forward  rate of return, respectively.   Red lines indicate Basel limit -- any firm return below the limit indicates a Basel breach given the bank leverage on the applicable date.}
\label{simulation}
\end{center}
\end{figure}

@@

 \cite{brownlees2015} define  systemic risk (SRISK) for a group of firms  at time $t$ as
\be{esrisk}
\mathrm{SRISK}_t\equiv\kappa\sum_i d_{it}|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+ \ ,
\ee
where  $\Es$ denotes  conditional expectation given a major general market downturn.  The proportionate contribution of firm $i$  to \eref{esrisk} is defined as the systemic risk in firm $i$  
 \be{sriskperc}
 \mathrm{SRISK}_{it}\equiv \frac{\pi_{it}|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+}{\Ex_d\{|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+\}}\cq \pi_{it}\equiv \frac{d_{it}}{d_t}\cq d_t\equiv \sum_i d_{it}\ , 
 \ee
where $\Ex_d$ denotes  debt weighted averaging at time $t$,  weighted averaging across firms $i$  using weights $\pi_{it}$.     Large $\mathrm{SRISK}_{it}$ indicates firm $i$ is systemically important: either because it holds a high proportion of the total debt, or it is unusually likely to breach the Basel capital requirement.  Expression \eref{sriskperc} depends on $\kappa$ through each of the $\ell_{it}$.

Given a general market downturn, the values of the puts $|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+$  in \eref{sriskperc} are known at time $t$:  there is no uncertainty except for possible  uncertainty in estimating the conditional  expected value.

Since
$$
|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+ \le\Es(|1-\e^{\nu_{it}-\ell_{it}}|^+)\ ,
$$
with equality  if  $\nu_{it}-\ell_{it}$ is concentrated on the negative axis.  If  $\nu_{it}>\ell_{it}$  has positive probability then the  inequality is strict.   Further $\mathrm{SRISK}_{it}$ in \eref{sriskperc}   is zero whenever
$$
\Es(\e^{\nu_{it}})\le\e^{\ell_{it}}\ .
$$
This inequality typically holds even if the expectation conditions on an extreme market downturn.

\section{Improved systemic risk measurement}

Following from \eref{bs}   define\footnote{Alternative terminology is the per unit capital shortfall put and the per unit expected capital shortfall.  For shortness we prefer the adjective Basel.  Note ``risk" here is not a probability but rather a measure of expected capital shortfall.} the  Basel put and  Basel risk of firm $i$ at time $t$ as
\be{put}
p_{it}\equiv |1-\e^{\nu_{it}-\ell_{it}}|^+\cq q_{it}\equiv \p(\nu_{it}\le \ell_{it})=\frac{\E(p_{it})}{\E(p_{it}|\nu_{it}\le \ell_{it})}\ ,
\ee
respectively, where $\E$ denotes unconditional expectation.  Note $0\le p_{it}\le 1$ with $p_{it}\rightarrow 0$ or 1 as $\nu_{it}\rightarrow\pm\infty$.
Further the Basel risk  $q_{it}$ increases as the distribution of $\nu_{it}$ moves to the left.  Both $\E(p_{it})$ and $q_{it}$ are thought of as probabilities of default with the former reflecting the whole distribution of $\nu_{it}$ given there is a default $\nu_{it}\le\ell_{it}$.

The total Basel put value  for firm  $i$ is   
$$
\kappa d_{it}\E(p_{it}) = \kappa d_{it}q_{it}\E(p_{it}|\nu_{it}\le \ell_{it})\ ,
$$
the cost of insuring firm $i$ does not breach the Basel standard.  In practice it may be appropriate to discount $p_{it}$ in \eref{put} by the interest rate over the period $(t,t+h)$ and value the put with risk neutral rather than normal expectation.

The put $p_{it}$ is tradable since, given $\kappa$, it relies only on the present leverage and the future return $\nu_{it}$ on equity $w_{it}$.  Market participants can value the put in  the same way as any other put and use the contract to diversify risk.  Firms can buy puts in the market to hedge Basel default risk.

However regulators will value the puts $p_{it}$ using a stressed, rather than risk neutral, expectation.   Stressed expectations correspond closely to conditional expectation given a system wide financial shock.    Regulators are concerned with the possibility of Basel breaches if such shocks occur and  have an  interest in monitoring stressed expectations.   In the extreme regulators can charge firms all or a  proportion of their stressed put values if there are implicit government bailout guarantees.

@@

In the above development $\E$  is  unstressed expectation:  that is expectation that does not assume a stressful scenario.   A stressed expectation, denoted $\Es$, is a
linear combination of  expectations, each assuming some level of stress
\be{formula}
 \Es(p_{it}) \equiv \E\{\phi\E(p_{it}|\phi)\} = \E(\phi p_{it}) = \E(p_{it}) + \cov\{\E(p_{it}|\phi),\phi\}\ .
\ee 
Here $\phi\ge 0$ with $\E(\phi)=1$ is a stress factor or ``stressor,"  defining events impacting $p_{it}$  and serving as a basis for stress testing.  Thus stress $\phi$ changes the expected value $\E(p_{it})$ by the covariance between the conditional expectation $\E(p_{it}|\phi)$  and the stressor $\phi$.

The conditioning variable $\phi$  downplays or highlight different scenarios.  The conditioning events are scenarios of interest and  probabilistic weighting is according to the level of interest.  The first equality in \eref{formula}  from the definition of conditional probability \citep{whittle2000probability}.  The second equality follows from
$$
\cov(p_{it},\phi)=\cov\{\E(p_{it}|\phi),\phi\}\ .
$$
The covariance is zero whenever  $p_{it}$ is independent of $\phi$ which occurs if $\phi=1$.

The stressed expectation \eref{formula}  is the mean of $p_{it}$  using the  density
\be{post}
\int \phi f(p_{it},\phi)\de \phi= \E(\phi|p_{it})f(p_{it})\cq \int \phi f(p_{it},\phi)\de \phi\de p_{it} = \E(\phi) = 1\ 
\  ,
\ee
where $f$ denotes density.  
Any outcome $p_{it}$ such that $\E(\phi|p_{it})$ is large  is amplified and vice versa.   To a Bayesian the density in the left  expression of $\eref{post}$ is a posterior density given a prior $f(p_{it})$ and ``likelihood" $\E(\phi|p_{it})$: more importance is given to outcomes   $p_{it}$  where $\phi$ is expected to be large.

@@

The right hand side of \eref{formula} splits the stressed expectation $\Es(p_{it})$ into two components: 
\be{vsstress}
\Es(p_{it}) =\mu_{it}+s_{it}\cq 
 \mu_{it} \equiv \E(p_{it})=q_{it}\E(p_{it}|\nu_{it}\le \ell_{it}) \ ,
\ee
$$
s_{it} \equiv \cov\{\E(p_{it}|\phi),\phi\}\cq q_{it} = \P(\nu_{it}\le \ell_it)\ , 
$$
called  the background stress  and systemic stress, respectively, in firm $i$ at time $t$.  Since both $\Es(p_{it})$ and $\E(p_{it})$ lie between 0 and 1 it follows both $\mu_{it}$ and $s_{it}$ lie between 0 and 1 and  are loosely interpreted as probabilities.  Further note 
$$
q_{it}\E(p_{it}|\nu_{it}\le \ell_{it}) \approx q_{it}\E(\ell_{it}-\nu_{it}|\nu_{it}\le \ell_{it}) = \ .
$$
and hence background risk decomposes into
$$
\mu_{it} \approx q_{it}\ell_{it} - \E(|\nu_{it}-\ell_{it}|^+)
$$
(Weihao, do you think it is worthwhile to decompose the $s_{it}$ analogously in terms of a probability time a tail event?)

The  term $\mu_{it}$  is called the background stress in firm $i$ and  reflects the log--leverage and the return volatility of firm $i$ at time $t$.  Background stress is unrelated to the stress factor $\phi$ and based on the unstressed distribution of the forward return $\nu_{it}$ and depends on the current view of the likely future progression of returns including their mean and volatility.     (Have to fill out discussion with how $mu_{it}$ measures the general uncertainty building up in the system with all  uncertainty  due to monitoring the system up to time $t$.)  Background stress is unrelated to the stress factor $\phi$.  Further
\be{mstress}
\mu_{it}=q_{it}\E(p_{it}|\nu_{it}\le \ell_{it})\ ,
\ee
where  $q_{it}$ is the Basel risk for  firm $i$  in the upcoming month,  while the second factor is the expected default size  (on a log scale)  if default occurs.
The probability $q_{it}$ depends on the  mean and volatility of daily returns at time $t$.

(*** unformed idea)   We can similarly decompose   (is this useful? -- Weihao can you look at this?)
$$
s_{it} = q_{\phi it}\E_\phi(p_{it}|\nu_{it}\le \ell_{it})-q_{it}\E(p_{it}|\nu_{it} \le \ell_{it})
$$

Firm $i$ is at Basel default if $\ell_{it}=0$  and then  $q_{it}\approx 1/2$.   As  $\ell_{it}$ increases from zero,  one month ahead Basel default status  becomes more certain since $\nu_{it}\le \ell_{it}$ becomes more certain and $q_{it}$ increases to 1.

@@

The second, systemic stress component $s_{it}$ in  \eref{vsstress},  captures the financial impact of a  hypothetical system wide financial shock.   The stress $\phi$ is systemic as it is expected to affect all firms $i$.  Further $s_{it}$ is the estimated   increase in put values on account of  $\phi$.   Examples of stress factors are given in \sref{marketstress} and \sref{genstress}.

>>>>

\makeatletter
\def\ps@pprintTitle{%
\let\@oddhead\@empty
\let\@evenhead\@empty
\def\@oddfoot{}%
\let\@evenfoot\@oddfoot}
\makeatother

@@

% Title of paper
\title{Measuring background and systemic risks in finance}
% List of authors, with corresponding author marked by asterisk
\author{Piet de Jong,  Geoff Loudon and Weihao Choo \\[4pt]
% Author addresses
\textit{Department of Applied Finance and Actuarial Studies\\ Macquarie University, Sydney, NSW 2109.}
\\[2pt]
%E-mail address for correspondence
{piet.dejong@mq.edu.au}}

@@

Recent literature in the area of quantitative systemic risk or stress measurement includes
\cite{adrian2011covar},
\cite{acharya2012capital},
\cite{acharya2012measuring},
 \cite{brownlees2010volatility} and \cite{brownlees2015}.   This study aims to extend and apply these techniques particularly in relation to the entities regulated by the Australian Prudential Regulation Authority (APRA). Thus our  broad aim is to develop, implement and bring to bear recent developments in systemic risk measurement and stress testing  on the aims of APRA and the CIFR targeted research areas.   (This needs much more commentary).

@@

Remaining sections are structured as follows. \sref{capshort} and \sref{futshort} define current and future  capital shortfall similarly as \cite{brownlees2015} under a simplistic Basel II regulatory framework. The definition of systemic risk used by \cite{brownlees2015} is discussed in \sref{srisk}, and is refined, extended and illustrated \sref{improve} to \sref{estimate}. \sref{marketstress} discusses specific stress examples which extend beyond \cite{brownlees2015}. Applications to Australian bank data are discussed in \sref{simulate} and \sref{simulate1}. \sref{aggregate} and \sref{aggregate1} discuss how stresses are combined across firms with and without allowance for merging or diversification. Generalised stressed are outlined in \sref{genstress}. \sref{riskmethod} offers an alternative modeling approach, based on assets. \sref{comparison} summarises differences between proposed stress measurement in this paper with that of 
\cite{brownlees2015}. \sref{conclude} concludes.

@@

\section{Capital shortfall and leverage}\label{capshort}

If $d_{it}$ and $w_{it}$ are the debt and equity of firm $i$ at time $t$ respectively and $\kappa$ is the prudential requirement,  then  capital shortfall at time $t$ is
\be{shortfall}
\kappa(d_{it}+w_{it}) - w_{it} = \kappa d_{it}  - (1-\kappa) w_{it} = \kappa d_{it}\left(1-\e^{-\ell_{it}}\right)\ ,
\ee
where
$$
\ell_{it} \equiv  \ln\frac{\kappa d_{it}}{(1-\kappa)w_{it}}= \ln\frac{d_{it}}{w_{it}}+\logit(\kappa) \cq \logit(\kappa)\equiv \ln \frac{\kappa}{1-\kappa} \ .
$$
The quantity $\ell_{it}$ is the adjusted log--leverage of firm $i$ at time $t$ and $\ell_{it}>0$ implies capital shortfall in \eref{shortfall} is positive. The parameter $\kappa$ is the proportion of assets $d_{it}+w_{it}$ excluded from capital calculations, and higher $\kappa$ leads to higher capital shortfall.
Assume\footnote{See for example \cite{brownlees2015}.   The value of $\kappa$ can and is varied to test for sensitivity etc.} $\kappa=0.08$ under Basel II implying $\logit(\kappa)=-2.44$ and  $\ell_{it}$ is the actual log--leverage minus 2.44.
The firm is in a Basel breach if actual  log leverage is above 2.44, otherwise it is Basel compliant.

\fref{Bloglev} displays Basel log--leverages ($\ell_{it}$ for $\kappa=0.08$) for the four major and four minor Australian banks listed in \tref{banks} on the first trading day of each month from January 2003  through to December 2014.  Note most banks are Basel compliant up to about 2008, entering into Basel breaches from 2009 as a result of the global financial crisis. Prolonged Basel breaches are experienced for particular banks, notably NAB.

\begin{figure}[htbp]
\begin{center}
\label{Bloglev}
\includegraphics{figures/bloglev.pdf}
\caption{Adjusted or Basel log--leverages for four major (left panel) and four minor (right panel) Australian banks from the beginning of 2003 through to end of 2014.  All banks contravene the threshold (corresponding to the zero horizontal) around the start of 2009.}
\end{center}
\end{figure}

\section{Future capital shortfall}\label{futshort}

Financial institutions and regulators are concerned with future Basel compliance and the likelihood of a  future Basel breach.   Future compliance depends on the future return on equity.   Consider  firm $i$ at time  $t+h$ where $h>0$.  Then\footnote{In the further development $\e^\nu$ is the continuously compounded return (including principal) and $\nu$  the  rate of return or log return.}
$$
\ell_{i,t+h} = \ln \frac{d_{i,t+h}}{w_{i,t+h}} +\logit(\kappa)= \ell_{it} -\nu_{it}\cq \nu_{it}\equiv \ln\frac{w_{i,t+h}}{w_{it}}  \ ,
$$
where it is assumed $d_{i,t+h}=d_{it}$.  Here $\nu_{it}$ is the log return on equity over $(t,t+h)$ and decreases adjusted log--leverage by the same amount.  The future return is unknown at time $t$ but its probability distribution is assumed to be well understood.

The capital  shortfall  at time $t+h$, ignoring the surplus portion, is,
\be{bs}
\kappa d_{it} \left|1-\e^{-\ell_{i,t+h}}\right|^+=\kappa d_{it} \left|1-\e^{\nu_{it}-\ell_{it}}\right|^+
\cq  |x|^+\equiv \max(0,x)\ .
\ee
Thus shortfall \eref{bs} is a $\kappa d_{it}$ multiplied by a put on the return $\e^{\nu_{it}-\ell_{it}}$  with strike 1.
The Basel  limit is reached at $t+h$ if $\nu_{it}=\ell_{it}$ and  breached  if
$\nu_{it}< \ell_{it}$.
A breach is  unlikely if $\ell_{it}$ is low i.e. either the log--leverage or prudential requirement $\kappa$ is low. This paper models future capital shortfall using log return on equity $\nu_{it}$ as it is typically available publicly. An alternative approach models future asset values $d_{i,t+h}+w_{i,t+h}$ in turn implying equity returns, and is briefly discussed in \sref{riskmethod}. Results in this paper generally hold for any modeling approach.

If there is a breach, $\nu_{it}<\ell_{it}$, then the amount in \eref{bs} makes up for the shortfall.   This amount may be cold comfort to regulators as it leaves the firm in a precarious position, teetering on the edge of non--compliance. Firms generally maintain a positive capital surplus to avoid breaches when unexpected shocks occur.

@@

To illustrate the setup in \eref{bs}, \fref{simulation}   displays two snapshot outputs from projections generated as described  in \aref{garchdcc}:  6000  simulated one month ahead projected returns for  CBA and the market, on  two dates: the first trading day in January 2009 and the first trading day in December 2014.    Both panels use the same horizontal and vertical scales.   Thus based on the available data at those two points in  time, policy makers and regulators faced entirely different projections based on the same time series model.   The scatter of dots are the forward simulations.  Note there is no hindsight bias as the model at each time point is based on the available data to that point in time.    The red horizontal line in each panel indicates the Basel limit:  any firm return less than the limit would constitute a Basel breach.   In the left panel there is little confidence that the Basel limit will be reached since it requires a return on equity approaching 20\% -- with confidence less than xxx the Basel standard will be breached.  In the right panel there is no chance of a Basel breach under any of the projected return on equity view -- the bank is ``safe."

 The black dots in each panel indicate the actual outcome after one month.    In the left panel the outcome is a decline in both  the market and CBA stock price.    In the right panel the returns are xxx and xxx.    Thus at the beginning of January  2009 CBA was projected to be far from compliance in a month while in December 2014 the one month projection is of complete compliance.

 The two panels  display very different volatility and slopes. In January 2009 both CBA and market return distributions are highly volatile and correlated. The correlation remains strong in December 2014 but with less return volatility. These snapshots are used to compute background and systemic stresses shown in subsequent sections.

\begin{figure}[htbp]
\begin{center}
\includegraphics{figures/simulation.pdf}
\caption{Forecast bivariate distribution of one month forward rates of return   for CBA (vertical axis) and the market rate of return (horizontal axis) at start of January 2009 (left panel)  and December 2014 (right panel). Note scales in both panels are the same, the relatively large volatility in the left panel, and the left skew in the  marginal distributions.  Yellow and black dots in each panel indicate origin (0,0) and  actual forward  rate of return, respectively.   Red lines indicate Basel limit -- any firm return below the limit indicates a Basel breach given the bank leverage on the applicable date.}
\label{simulation}
\end{center}
\end{figure}

@@

 \cite{brownlees2015} defines  systemic risk (SRISK) for a group of firms  at time $t$ as
\be{esrisk}
\mathrm{SRISK}_t\equiv\kappa\sum_i d_{it}\left|1-\Es(\e^{\nu_{it}-\ell_{it}})\right|^+ \ ,
\ee
where  $\Es$ denotes expectation given a major general market downturn. Hence the expected capital shortfall (allowing surplus offset) is computed from \eref{shortfall} assuming a market downturn and added across all firms. Firms having a expected capital surplus are ignored. The systemic risk of firm $i$ at time $t$ is its proportionate contribution to \eref{esrisk}:
 \be{sriskperc}
 \mathrm{SRISK}_{it}\equiv \pi_{it}\frac{|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+}{\Ex_d\{|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+\}}\cq \pi_{it}\equiv \frac{d_{it}}{d_t}\cq d_t\equiv \sum_i d_{it}\ ,
 \ee
where $\Ex_d$ denotes weighted averaging across firms $i$ using weights $\pi_{it}$.     Large $\mathrm{SRISK}_{it}$ indicates firm $i$ is systemically important: it holds a high proportion of the total debt, and it is likely to heavily breach the Basel capital requirement compared to remaining other firms.  Expression \eref{sriskperc} depends on $\kappa$ through each of the $\ell_{it}$.

Given a general market downturn, put values $|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+$  in \eref{sriskperc} are known at time $t$:  there is no uncertainty except for possible  uncertainty in estimating the conditional  expected value.

Using the Jensen's inequality,
$$
\left|1-\Es(\e^{\nu_{it}-\ell_{it}})\right|^+ \le\Es\left(\left|1-\e^{\nu_{it}-\ell_{it}}\right|^+\right)\ ,
$$
with equality  if  $\nu_{it}-\ell_{it}$ is concentrated on the negative axis.  If  $\nu_{it}>\ell_{it}$  has positive probability then the  inequality is strict.   Further $\mathrm{SRISK}_{it}$ in \eref{sriskperc}   is zero whenever
$$
\Es(\e^{\nu_{it}})\ge\e^{\ell_{it}}\ .
$$
This inequality typically holds even if the expectation conditions on an extreme market downturn. The above two inequalities suggest SRISK is not risk sensitive and leads to refinements discussed in the next section.

\section{Improved systemic risk measurement}\label{improve}

Following from \eref{bs}   define\footnote{Alternative terminology is the per unit capital shortfall put and the per unit expected capital shortfall.  For shortness we prefer the adjective Basel.  Note ``risk" here is not a probability but rather a measure of expected capital shortfall.} the  Basel put payoff and default probability of firm $i$ at time $t$ respectively as
\be{put}
p_{it}\equiv \left|1-\e^{\nu_{it}-\ell_{it}}\right|^+\cq q_{it}\equiv \p(\nu_{it}\le \ell_{it})=\frac{\E(p_{it})}{\E(p_{it}|\nu_{it}\le \ell_{it})}\ ,
\ee
where $\E$ denotes expectation without any imposed stress.  Note $0\le p_{it}\le 1$ with $p_{it}\rightarrow 0$ or 1 as $\nu_{it}\rightarrow\pm\infty$.
Further $q_{it}$ increases as the distribution of $\nu_{it}$ moves to the left.  Both $\E(p_{it})$ and $q_{it}$ measure default risk between 0 and 1, with the former reflecting the conditional distribution of $\nu_{it}$ below $\ell_{it}$ and the latter only concerned with the probability mass in the same area.

The monetary Basel put value  for firm  $i$ is the total expected payout
$$
\kappa d_{it}\E(p_{it}) = \kappa d_{it}q_{it}\E(p_{it}|\nu_{it}\le \ell_{it})\ ,
$$
the expected cost of insuring firm $i$ against a Basel breach.  The expression on the right is the product of four terms: the capital requirement $\kappa$, firm debt $d_{it}$, probability of Basel default $q_{it}$, and the expected payout if a default occurs (against a standardised exercise price of 1). In practice it may be appropriate to discount $p_{it}$ in \eref{put} by the interest rate over the period $(t,t+h)$ and value the put with risk neutral rather than normal expectation.

The put $p_{it}$ is tradable since, given $\kappa$, it relies only on the present leverage and the future return $\nu_{it}$ on equity $w_{it}$.  Market participants can value the put in  the same way as any other put and use the contract to diversify risk.  Firms can buy puts in the market to hedge their Basel default risk, or contribute an amount equal to the put value into a bailout pool.

Regulators are inclined to value the puts $p_{it}$ using a stressed, rather than risk neutral, expectation.   Stressed expectations correspond closely to conditional expectation given a system wide shock.    Regulators are concerned with the possibility and extent of Basel breaches if such shocks occur and  have an  interest in monitoring stressed expectations across firms and time.   In the extreme regulators can charge firms all or a  proportion of their stressed put values if there are implicit government bailout guarantees.

@@

In the above development $\E$  is  unstressed expectation and does not assume a stressful scenario.   A stressed expectation, denoted $\Es$, is a
linear combination of a range of conditional expectations each assuming some level of stress:
\be{formula}
 \Es(p_{it}) \equiv \E\{\phi\E(p_{it}|\phi)\} = \E(\phi p_{it}) = \E(p_{it}) + \cov\{\E(p_{it}|\phi),\phi\}\ .
\ee
Here $\phi\ge 0$ with $\E(\phi)=1$ is a random stress factor or ``stressor,"  with different values re-weighting, and corresponding to, scenarios impacting $p_{it}$.  Thus stress $\phi$ increases the expected value $\E(p_{it})$ by the covariance between the conditional expectation $\E(p_{it}|\phi)$  and the stressor $\phi$. A larger covariance results if higher values of $\phi$, corresponding to increasingly stressed scenarios, lead to larger put values. The covariance is zero if $p_{it}$ does not vary with the different scenarios indicated by $\phi$, or under the trivial case $\phi=1$ where scenarios are not re-weighted. The impact of $\phi$ is formalised in \eref{post} below. Examples of $\phi$ implying various stress calculations are shown in subsequent sections. Weighted expectations in the form of \eref{formula} are discussed in \cite{choo2010determining} and \cite{furman2008weighted1}.

The first equality in \eref{formula} follows from the definition of conditional probability \citep{whittle2000probability}.  The second equality follows from
$$
\cov(p_{it},\phi)=\cov\{\E(p_{it}|\phi),\phi\}\ .
$$

The stressed expectation \eref{formula}  is the mean of $p_{it}$  using a stressed density
\be{post}
\int \phi f(p_{it},\phi)\de \phi= \E(\phi|p_{it})f(p_{it})\cq \int\int \phi f(p_{it},\phi)\de \phi\de p_{it} = \E(\phi) = 1\
\  ,
\ee
where $f$ denotes the density of the quantity in parentheses.
Hence the likelihood of any outcome $p_{it}$ such that $\E(\phi|p_{it})$ is large is amplified and vice versa.   To a Bayesian the density in the left  expression of $\eref{post}$ is a posterior density given a prior $f(p_{it})$ and ``likelihood" $\E(\phi|p_{it})$: more importance is given to outcomes   $p_{it}$  where $\phi$ is expected to be large.

@@

The right hand side of \eref{formula} splits the stressed expectation $\Es(p_{it})$ into two components:
\be{vsstress}
\Es(p_{it}) =\mu_{it}+s_{it}\cq
 \mu_{it} \equiv \E(p_{it})=q_{it}\E(p_{it}|\nu_{it}\le \ell_{it}) \ ,
\ee
$$
s_{it} \equiv \cov\{\E(p_{it}|\phi),\phi\}\ ,
$$
called  the background stress  and systemic stress, respectively, in firm $i$ at time $t$. Both $\mu_{it}$ and $s_{it}$ are computed from the current adjusted log--leverage and the forward return distribution at time $t$. In addition $0\le \mu_{it},\mu_{it}+s_{it}\le 1$ and $s_{it}\ge 0$ typically holds unless firm $i$ benefits from a stress in the system. Applying a Taylor series expansion of the exponential function on $p_{it}$ yields
$$
\E(p_{it}|\nu_{it}\le \ell_{it}) \approx \ell_{it}-\E(\nu_{it}|\nu_{it}\le \ell_{it})\ ,
$$
and hence background stress decomposes into
$$
\mu_{it} \approx q_{it} \left\{\ell_{it} - \E(\nu_{it}|\nu_{it}\le \ell_{it})\right\} \ ,
$$
which is increasing in the Basel default probability $q_{it}$, adjusted log--leverage $\ell_{it}$ and the left skewness of $\nu_{it}$ as measured by the lower tail conditional expectation. If $\ell_{it}=0$  and then firm $i$ is at Basel default at time $t+h$ if  $\nu_{it}<0$ with probability $q_{it}\approx 1/2$. As  $\ell_{it}$ increases,  one month ahead Basel default becomes more certain since $\nu_{it}\le \ell_{it}$ becomes more certain and $q_{it}$ increases to 1. Background stress is unrelated to the stress factor $\phi$ and based on the unstressed distribution of the forward return $\nu_{it}$: the current view of the future progression of returns including their mean and volatility.

Similarly decompose systemic stress
$$
s_{it} = q_{\phi it}\E_\phi(p_{it}|\nu_{it}\le \ell_{it})-q_{it}\E(p_{it}|\nu_{it} \le \ell_{it})
$$
where $q_{\phi it}$ is the default probability implied from the stressed density in \eref{post}. The stress typically increases both the default probability  $q_{\phi it}$ and the conditional expected default $\E_\phi(p_{it}|\nu_{it}\le \ell_{it})$ relative to the unstressed quantities $q_{it}$ and $\E(p_{it}|\nu_{it} \le \ell_{it})$. Greater sensitivity of firm $i$ to market wide stresses leads to higher systemic stress $s_{it}$.

Monitoring $\mu_{it}$ across the market provides a leading indication of the level of background stress and anticipates buildups such as shortly before the 2008 global financial crisis. The aggregation of put values and stresses across the market is discussed and illustrated below. An increase in $\mu_{it}$ indicates either higher probabilities of defaults or larger capital shortfalls if defaults occur. Introducing systemic stress $s_{it}$ increases stress-sensitivity in two ways. Firstly adverse scenarios are emphasized which would otherwise be less obvious in $\mu_{it}$. Secondly, as $\phi$ is a market based stressor, system wide defaults and shortfalls resulting from market dependencies are emphasized and revealed.

\begin{comment}
Further
\be{mstress}
\mu_{it}=q_{it}\E(p_{it}|\nu_{it}\le \ell_{it})\ ,
\ee
where  $q_{it}$ is the Basel risk for  firm $i$  in the upcoming month,  while the second factor is the expected default size  (on a log scale)  if default occurs.
The probability $q_{it}$ depends on the  mean and volatility of daily returns at time $t$.
\end{comment}

@@

The second, systemic stress component $s_{it}$ in  \eref{vsstress}  captures the financial impact of a  hypothetical system wide financial shock.   The stress $\phi$ is systemic as it is expected to affect all firms $i$.  Further $s_{it}$ is the estimated   increase in put values on account of  $\phi$.   Examples of stress factors are given in \sref{marketstress} and \sref{genstress}.
